Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:14	13:18:07	(Wed14.Oct)

\newcommand\mediaPath{gfx/media}
\newcommand\mediaI{\multimedia{\mediaPath/media1.mp4}{Media Movie 1}}
\newcommand\mediaII{\multimedia{\mediaPath/media2.mp4}{Media Movie 2}}

@@

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This makes MVDR impracticable and sometimes infeasible. We have shown in previous studies that MVDR's complexity can be reduced, and its implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}. However, even with a near optimal implementation it is still slow compared to DAS.

A very fast and simple alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. It was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR in a system with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions up to 3 windows by e.g. Stankwitz in radar imaging~\cite{Stankwitz1995}, but unlike these LCA more windows, and add micro-steered variations of them.

>>>>

% \newcommand\mediaPath{gfx/media}
\newcommand\mediaPath{http://folk.uio.no/joibu/media/2015_JOE_LCA}

\newcommand\mediaI{\multimedia{\mediaPath/media1.mp4}{Media Movie 1}}
\newcommand\mediaII{\multimedia{\mediaPath/media2.mp4}{Media Movie 2}}

@@

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This makes MVDR impracticable and sometimes infeasible. We have shown in previous studies that MVDR's complexity can be reduced, and its implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}. However, even this near optimal implementation is slow compared to DAS.

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. It was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in a system with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions up to 3 windows by e.g. Stankwitz in radar imaging~\cite{Stankwitz1995}, but unlike these LCA more windows, and add micro-steered variations of them.
